A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-07-08 paper/elsarticle/elsarticle-template.tex
paper

\begin{figure}
    \centering
    %\subfloat[\centering Initial virtual projector.]{{\includegraphics[height=3.25cm]{images/1.png} }}
    %\qquad
    \subfloat[\centering Virtual camera.]{{\includegraphics[height=4.5cm]{images/2.png}}}
    \qquad
    \subfloat[\centering Virtual projector.]{{\includegraphics[height=4.5cm]{images/3.png}}}
    \caption{Obtaining the virtual projector. (a) The virtual camera is obtained by rotating the camera about its center of projection such that its optical axis be made parallel with the normal vector of the scene plane. (b) The virtual projector is obtained by (i) rotating the projector about the point of intersection of its optical axis with the scene plane such that its optical axis be made parallel with the scene plane's normal, (ii) rotating the $X$- and $Y$-axes to render them parallel with those of the virtual camera, and (iii) translating to achieve the desired projected image dimensions.}
    \label{fig:virtualproj}
\end{figure}

>>>>

\begin{figure}
    \centering
    %\subfloat[\centering Initial virtual projector.]{{\includegraphics[height=3.25cm]{images/1.png} }}
    %\qquad
    \subfloat[\centering Virtual camera.]{{\includegraphics[height=4.5cm]{images/2.png}}}
    \qquad
    \subfloat[\centering Virtual projector.]{{\includegraphics[height=4.5cm]{images/3.png}}}
    \caption{Obtaining the virtual projector. (a) The virtual camera is obtained by rotating the camera about its center of projection such that its optical axis be made parallel with the normal vector of the scene plane. (b) The virtual projector is obtained by (i) rotating the projector about the point of intersection of its optical axis with the scene plane such that its optical axis be made parallel with the scene plane's normal, (ii) rotating the $X$- and $Y$-axes to render them parallel with those of the virtual camera, and (iii) optionally translating to achieve the desired projected image dimensions. The virtual projector is thus made fronto-parallel with the ground plane and axially aligned with the virtual camera.}
    \label{fig:virtualproj}
\end{figure}
